\documentclass[10pt]{report}
\usepackage[utf8]{inputenc}

\input{general_preamble}

% DEFINE TITLE STYLES
\makeatletter 
\renewcommand\maketitle{
{\begin{center}
{\Large \bfseries \@title }\\
{\small \emph{First created}: \DTMdisplaydate{2025}{03}{25}{-1}\hfill%
\setstretch{1.0} \small \hfill \emph{Last update}: \today}
%{\Large  \@author}\\[4ex] 
\end{center}}} % Note the extra }
\makeatother

%-------------------------------------------------------------------------

\begin{document}

%\sisetup{parse-numbers = false}
\DTMsetdatestyle{cvdateformat}

\title{\vspace{-3em} Multiplexed mRNA \textit{in-situ} Hybridization Chain Reaction (HCR) in \emph{Pleurobrachia pileus} adult tissues}
\maketitle
\thispagestyle{plain}
\markboth{HCR in \emph{Pleurobrachia} tissues}{}

\section*{\vspace{-1em} \textendash{} Protocol \textendash{}}
\markright{Protocol}

\subsection*{Day 1 \textendash{} Sample preparation}

\alert{In each step, samples can be rocked on a nutator or on an orbital (horizontal) shaker.}

\begin{enumerate}[series = steps]
	\item Dissect the desired aadult tissue in 100\% methanol.
	\item Wash samples for \underline{\quarter} each with a graded series of \fivehunmicrol{} (or \onemil) of \textbf{methanol (\qtylist{60;30}{\percent}) in PBST}.
	\item \step{wash}{\quarter}{\fivehunmicrol{} (or \onemil)}{PBST}{RT}
	\item \step{rock}{\qty{2}{\minute}}{\fivehunmicrol{} (or \onemil)}{\qty{2.6}{\ug\per\ml} proteinase K}{RT}
	\item \item \step{wash}{\quarter}{\fivehunmicrol{} (or \onemil)}{PBST}{RT}
\end{enumerate}

\bigskip\alert{Pre-heat probe-hybridization buffer to \thirtysevendegree{} (you will need \fivehunmicrol per tube [\qty{250}{\ul} for the pre-hybridization, and \qty{250}{\ul} for the probe solution]).}
	
\subsection*{Day 1 \textendash{} HCR detection stage}
\begin{enumerate}[series = steps]
	\item \step{pre-hybridize}{\halfhour}{\fivehunmicrol}{pre-warmed probe hybridization buffer}{\thirtysevendegree}
\end{enumerate}

\bigskip\alert{If reusing probes, pre-warm probe solution to \thirtysevendegree, then skip to Step 3.}

\alert{At this step, samples can be stored in probe hybridization buffer at \minustwenty{} for several months.}

\begin{enumerate}[resume = steps]
	\item Prepare probe solution by adding \qty{0.8}{\ul} (\qty{0.8}{\pmol}) of each \textbf{probe set \qty{1}{\micro\molar} stock solution} to \twohunmicrol{} of \textbf{probe hybridization buffer} (final concentration of \qty{4}{\nano\molar}) at \thirtysevendegree.\\
	      \note{if using \fivehunmicrol{} of probe solution, add \qty{2}{\ul} (\qty{2}{\pmol}) of each probe set.}
	\item \step{incubate}{\qty{> 12}{\hour} (overnight)}{\twohunmicrol}{pre-warmed probe solution}{\thirtysevendegree}
\end{enumerate}

\bigskip\alert{Pre-heat probe wash buffer at \thirtysevendegree{} (you will need \fivehunmicrol per tube per 4 washes).}


\subsection*{Day 2 \textendash{} HCR amplification stage}

\alert{Pre-equilibrate amplification buffer to room temperature (you will need \qty{700}{\ul} per tube [\fivehunmicrol{} for pre-amplification, and \twohunmicrol{} for the hairpin solution]).}
\begin{enumerate}[series = steps]
	\item \step{wash}{\qtytimes{4}{20}{\minute}}{\fivehunmicrol}{probe wash buffer}{\thirtysevendegree}
\end{enumerate}

\bigskip\alert{Probe solution can be saved and reused for 2--3 times; store at \minustwenty.}

\begin{enumerate}[resume = steps]
	\item \step{wash}{\qtytimes{3}{5}{\minute}}{\fivehunmicrol{} (or \onemil)}{\ssct}{RT}
	\item \step{pre-amplify}{\halfhour}{\fivehunmicrol}{amplification buffer}{RT}
	\item Snap cool in separate tubes \qty{4}{\ul} of \textbf{hairpin H1} (\qty{30}{\pmol}) and \qty{4}{\ul} of \textbf{hairpin H2} (\qty{30}{\pmol}) \textbf{\qty{3}{\micro\molar} stock solutions}: heat at \qty{95}{\degreeCelsius} for \qty{90}{\s} and cool to RT in the dark for \halfhour.
	      %\note{doubling hairpin concentration can help to boost signal.}
\end{enumerate}

\bigskip\alert{If reusing hairpin solutions, heat at \qty{95}{\degreeCelsius} and cool at RT, then skip at Step 6.}

\begin{enumerate}[resume = steps]
	\item Prepare hairpin solution by adding \textbf{snap-cooled H1 hairpins} and \textbf{snap-cooled H2 hairpins} to \twohunmicrol{} of \textbf{amplification buffer} (final concentration of each hairpin of \qty{60}{\nano\molar}) at RT.\\
	      \note{if using \qty{100}{\ul} of amplification buffer, add \qty{2}{\ul} (\qty{15}{\pmol}) of each hairpin.}\\
	      \note{if using \qty{500}{\ul} of amplification buffer, add \qty{10}{\ul} (\qty{75}{\pmol}) of each hairpin.}
	\item \step{incubate}{\qty{>12}{\hour} (overnight)}{\twohunmicrol}{hairpin solution}{RT}
\end{enumerate}

\subsection*{Day 3 \textendash{} HCR conclusion}

\begin{enumerate}[series = steps]
	\item \step{wash}{\qtytimes{2}{5}{\minute}, \qtytimes{2}{30}{\minute}, and \qtytimes{1}{5}{\minute}}{\fivehunmicrol{} (or \onemil)}{\ssct}{RT}
\end{enumerate}

\bigskip\alert{Hairpin solution can be saved and reused for 2--3 times; store at \minustwenty.}
\alert{At this step, samples can be stored in the dark in \ssct for several days at room temperature.}

\subsection*{Day 3 \textendash{} Sample mounting}

\begin{enumerate}[series = steps]
	\item \step{wash}{\qtytimes{3}{5}{\minute}}{\fivehunmicrol{} (or \onemil)}{\pbs}{RT}
\end{enumerate}

\bigskip\alert{If using VECTASHIELD\textregistered{} PLUS Antifade Mounting Medium with DAPI (H-2000), skip directly to Step 4.}

\begin{enumerate}[resume = steps]
	\item \step{incubate}{\qty{20}{\minute}}{\fivehunmicrol{} (or \onemil)}{DAPI staining solution}{RT}
	\item \step{wash}{\qtytimes{3}{5}{\minute}}{\fivehunmicrol{} (or \onemil)}{\pbs}{RT}
	\item \step{incubate}{\qtyrange{30}{60}{\minute}}{\onemil}{\qty{50}{\percent} glycerol in \pbs}{RT}
	\item \step{incubate}{\qtyrange{30}{60}{\minute}}{\onemil}{\qty{75}{\percent} glycerol in \pbs}{RT}
\end{enumerate}

\bigskip\alert{Maintaining samples at pH 7.40 is critical for the stability of fluorophores and long-term storage of mRNA \textit{in-situ} HCR samples.}
\alert{At this step, samples can be stored in the dark in \qty{75}{\percent} glycerol for several month at \fourdegree.}

\begin{enumerate}[resume = steps]
	\item Collect precipitated samples from the \qty{75}{\percent} glycerol solution and place them on a cleaned (bridged, if necessary) slide.
	\item Add \qtyrange{\sim 15}{20}{\ul} of mounting medium (or VECTASHIELD\textregistered{} PLUS Antifade Mounting Medium with DAPI [H-2000]) directly on samples.
\end{enumerate}

\bigskip\alert{Adjust the amount of embryo suspension and mounting medium according to the cover glass dimensions, the quantity of samples, and the thickness of the bridge.}

\begin{enumerate}[resume = steps]
	\item	Seal the slide with nail polish and store in the dark at \fourdegree.
\end{enumerate}

\clearpage


